Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-04-18 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
add code for multi panel plot

@@

# Multi panel plots
Richness maps
# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness_sub.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness_sub.csv"))
```

>>>>

## 10 km
ADD CODE HERE!!!

@@

# Multi panel plots
Richness maps
```{r}
grid.arrange(plot_1, plot_2, nrow = 1)
```

# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness_sub.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness_sub.csv"))
```
